%\documentclass[journal]{IEEEtran}
\documentclass{article}

\usepackage[textwidth=8.5in, textheight=11in, top=1.5in, bottom=1.5in, left=1in, right=1in]{geometry}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
% equalize two columns in the last page
\usepackage{flushend}

\usepackage{url}
%\usepackage[caption=false]{subfig}
\usepackage{subfigure}
\usepackage{array}
\usepackage{color}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{multicol}

\usepackage{algorithm}
\usepackage{algpseudocode}
\renewcommand{\algorithmicforall}{\textbf{for each}}
% \usepackage{setspace} % squeeze the vertical space in algorithm

% \makeatletter
% \renewcommand{\ALG@beginalgorithmic}{\small}
% \makeatother

\usepackage{amsmath}
% \usepackage{amsthm}
\usepackage{amssymb}
\usepackage{stmaryrd}


\newcommand{\squishlist}{
\begin{list}{$\bullet$}
{ \setlength{\itemsep}{0pt}
\setlength{\parsep}{3pt}
\setlength{\topsep}{3pt}
\setlength{\partopsep}{0pt}
\setlength{\leftmargin}{1.5em}
\setlength{\labelwidth}{1em}
\setlength{\labelsep}{0.5em} } }

\newcommand{\squishend}{  \end{list}  }

% shortcut
\usepackage{xspace}
\newcommand{\etc}{{etc.}\@\xspace}
\newcommand{\ie}{{i.e.,}\@\xspace}
\newcommand{\etal}{{et al.}\@\xspace}
\newcommand{\eg}{{e.g.,}\@\xspace}
\newcommand{\aka}{{aka}\@\xspace}

\newcommand{\termspace}{{\vspace{-0.15in}}}         
% control space after figure
%\newcommand\figsize{0.8\linewidth}
\newcommand\assize{1.3}
\newcommand\tablefontsize{\small}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\usepackage{graphicx}
\graphicspath{{figs/}}

\usepackage{indentfirst}
\usepackage{fixltx2e}
\newcommand{\wu}[1] {\textbf{\color{blue}{Wu: #1}}}
\newcommand{\tsub}[1]{\textsubscript{#1}}

\usepackage{multirow}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\begin{document}

\title{Measurement of Crowdsourced Live Video on Server Side}

%\author{Jianer Zhou$^\dag$ $^\S$, Zhenyu Li$^\dag$, Qinghua Wu$^\dag$, Gaogang Xie$^\dag$ \\
%$^\dag$ICT-CAS, China,
%$^\S$Univ. of CAS, China\\
%\{zhoujianer, zyli, wuqinghua, xie\}@ict.ac.cn}
\author{}
\date{}
\maketitle

\begin{abstract}
As the popularity of intelligent medium device and improvement of bandwidth, more and more people are involved in the crowdsourced live video applications. Despite its great popularity, crowdsourced live video system in the wild has not been widely studied. This motivate us to analyze the the performance of a crowdsourced live video system in production network. In this work, we measure the effectiveness of this system through a packet-level trace collected from server side. We find that video upload process is the key of the overall performance as it influences the video download throughput and 37 \% of stalls in upload process cause stalls in download flows. Our findings provide new insights in such system and can help the designers to improve its effectiveness.
\end{abstract}

\input{introduction}
\input{system}
%\input{datasets}
\input{system-measurement}
\input{frame-analysis}
%\input{related}
\input{summary}
\input{conclusion}

\bibliographystyle{abbrv}
% \small
\bibliography{reference}

\end{document}
